A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.Rnw
Added reference to HTCondor
Closes #133

Volunteer computing involves users deciding to run a program that acts
as a client or as a peer in an experiment
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}. However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in [citation hidden]. 
%\cite{DBLP:conf/gecco/GuervosG15}.

>>>>

Volunteer computing involves users deciding to run a program that acts
as a client or as a peer in an experiment
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home} or
high-throughput queuing system that such as HTCondor \cite{HTCondor}.
However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in [citation hidden]. Systems based on the
JavaScript/browser combination
emphasize the ephemerality, ease of use and universality, while
systems such as HTCondor or BOINC might be more adequate for work that
require higher availability of volunteer resources, achieving this
with downloadable clients, in some cases like HTCondor needing
administration access to the resources.
%\cite{DBLP:conf/gecco/GuervosG15}.
